We analyze the influence of linear redshift space distortion (RSD) in kSZ signal reconstruction. 
%After knowing this, we provide the very interesting result of taking advantage of the effect to get better cross correlation(Fig.\ref{fig:r}).
Equipped with it, we provide the very interesting results of adding RSD to simulations, 
and get better cross correlation (Fig.\ref{fig:r}). 
We also discuss another important advantage RSD brings.

The redshift distortions results from the radial peculiar velocity, 
which leads to a misjudgement of distance referring to Hubble flow.
%$\chi^{RSD}=\chi+\frac{v_z}{H}$, 
%where $\chi$ is the radial distance, $v_z$ is the parallel peculiar velocity.

In linear regions, it will induce an extra density contraction in redshift space:
\begin{eqnarray}
\label{eq:rsd}
\delta^{RSD}(\bm{k})\approx (1+f\frac{k_z^2}{k^2})\delta(\bm{k})\,
\end{eqnarray}
where again $f=\frac{d\mathrm{ln}D}{d\mathrm{ln}a}$, 
with the cosmological parameter we choose, $f=1.5, z\sim1; f=0.96, z\sim2$. 

Therefore, the easiest way to substract the linear RSD is to 
devide the $\delta^{RSD}$ we have by $1+f\frac{k_z^2}{k^2}$ 
before all the calculations.

However, if we leave it here, since our foreground is in the same direction as the RSD, we will see some fortunate good effects.
%However, in our case, we have the foreground of the same direction as the RSD, we just leave it here and see the miracular effect it brings. 
We discuss both the case of non-tidal reconstruction, 
and tidal reconstruction, and they are improved in different ways. 

Note: in the following argument, small k refers to $k\sim 0.01h/Mpc$, larger k refers to $k>0.1h/Mpc$, the powerspectrum of latter is around a magnitude smaller than the former.

(1) $\hat \Theta$ with RSD foreground substracted 21cm density field $\delta_{fs}^{RSD}$.

Following Eq.(\ref{eq:v}), we can quickly write down the change for v(k):
\begin{eqnarray}
    \hat v_{z,fs}^{RSD}(\bm{k})\propto \delta^{RSD}_{fs}(\bm{k})\frac{k_z}{k^2}\\
    =\hat v_{z,fs}(\bm{k})(1+f\frac{k_z^2}{k^2})
\end{eqnarray}
The new term gives heavier weigh to modes with $k_\parallel\gg k_\perp$.

The real kSZ signal in Fourier space reads:
\begin{eqnarray}
    \Theta(\bm{k_\perp})\equiv \Theta(k_x,k_y,0)\propto\int d^3k&\delta(\bm{k_\perp}-\bm{k}) v_z(\bm{k})\\
    \propto\int d^3k&\delta(\bm{k_\perp}-\bm{k})\delta(\bm{k})\frac{k_z}{k^2}\nonumber
\end{eqnarray}
For foreground substracted field the kSZ signal in Fourier space becomes:
\begin{eqnarray}
    \Theta_{fs}^{RSD}(\bm{k_\perp})
%    \propto\int d^3k&\delta(\bm{k_\perp}-\bm{k}) v_{z,fs}^{RSD}(\bm{k})\\
    \propto\int d^3k&\delta(\bm{k_\perp}-\bm{k})\delta_{fs}(\bm{k})\frac{k_z}{k^2}(1+f\frac{k_z^2}{k^2})
\end{eqnarray}
Notice, the first $\delta$ we use the original field, since this is the quantity we want to obtain in real cross correlating procedures.

{\it seems to need a powerspectrum of $P_\delta$}

When $k_\perp$ is small: 

In original kSZ signal, $\delta(\bm{k_\perp}-\bm{k}),\delta(\bm{k}),\frac{k_z}{k^2}$ reaches peak nearly at the same point when both $k_\perp,k\parallel$ are small, and this dominates the signal. 
However, in the case of foreground substracted field, 
$\delta_{fs}$ is seriously reduced at small $k_\parallel$, 
and $\Theta_{fs}$ hense comes more from larger $k_\parallel$ 
which has little correlations with the original kSZ.

Fortunately, the RSD gives another term $1+f\frac{k_z^2}{k^2}$, 
which give additional weigh to smaller $k_\parallel$ 
and partly compensate the weigh loss in foreground substraction. 
Therefore, we could have slightly better correlations in small $k_\perp$.

When $k_\perp$ is large:

$\delta(\bm{k_\perp}-\bm{k})$ and $\delta(\bm{k})$ 
no longer reach the peak simultaneously, 
and $\Theta$ comes from sum of a series of $k\prime$ from small to larger, 
hense the foreground substraction does not matter as much as in the case of $k_\parallel$, 
so both RSD and non-RSD case will have cross correlation.

(2) RSD influence to tidal reconstruction

After adding linear RSD, Eq.(\ref{eq:gamma}), each term will have two new weigh in Fourier space.

For simplicity, 
we define a demonstrator $\hat\gamma_{i,j}^{RSD}(\bm{x})\equiv\delta_{RSD}^{w_i}(\bm{x})\delta_{RSD}^{w_j}(\bm{x})$. 

In Fourier space, it becomes:
\begin{subequations}
\begin{align}
\hat\gamma_{RSD}(\bm{k})    
=&\int \frac{d^3k\prime}{(2\pi)^3}\delta^{w_i}(\bm{k}-\bm{k}\prime)\delta^{w_j}(\bm{k}\prime)\label{eq:rsd1}\\
 &(1+f\frac{(\bm{k}-\bm{k}\prime)_z^2}{(\bm{k}-\bm{k}\prime)^2})(1+f\frac{k\prime_z^2}{k\prime^2})\nonumber\\
=&\int \frac{d^3k\prime}{(2\pi)^3}
\delta_{fs}(\bm{k}-\bm{k}\prime)S(|\bm{k}-\bm{k}\prime|)\delta_{fs}(\bm{k}\prime)S(k\prime)\label{eq:rsd2}\\
&\frac{(\bm{k}-\bm{k}\prime)_i}{|\bm{k}-\bm{k}\prime|}\frac{k\prime_j}{k\prime}
(1+f\frac{(\bm{k}-\bm{k}\prime)_z^2}{(\bm{k}-\bm{k}\prime)^2})(1+f\frac{k\prime_z^2}{k\prime^2})\nonumber
\end{align}
\end{subequations}
From \eqref{eq:rsd1} we can see that the shear estimators now favor 
information from $\delta(k)$ with $k\_parallel\gg k_\perp$ more than before.

From \eqref{eq:rsd2} we see the influence on different gamma varies. 
The amplification will be maximized 
when the shape of the two new weigh $(1+f\frac{k_z}{k^2}$ 
at most approches other terms, 
i.e. when $i=j=z$. 
Therefore $\hat\gamma_z$ will be influenced most, followed by $\hat\gamma_x,\hat\gamma_y$

In all, the RSD effect is a natual filter that weighs more the information on z direction, and down-weigh the information of large $k_\perp$ to small $k_\perp$.

Therefore, if we use 2D tidal reconstruction, RSD will cause a noticeable degration on the reconstruction (% refer to mao's paper)
If we have RSD yet not have foreground, apply 3D tidal reconstruction, 
RSD may cause slight degration with  
However, fortunately, 
we have foreground which happen to be in the same direction with RSD. 
For z directions, only small $k_\parallel$ modes are lost, which do not matter much in the reconstruction;
while for other directions sufficient amount of modes with $k_\perp$ from small to large are lost, 
and this leads to more inaccurate reconstruction on $k_\perp$ direction. 
And RSD serve as a natural filter to deal with that. \ref{fig:v}


